\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,mathtools,nccmath}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\usepackage{braket}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\qbit}{\ensuremath|\psi\rangle}
\newcommand{\qbitv}{\ensuremath|\varphi\rangle}
\newcommand{\qz}{\ensuremath|0\rangle}
\newcommand{\qo}{\ensuremath|1\rangle}
\renewcommand{\d}{\, \mathrm{d}}

\newtheorem{definition}{Definition}[section]

\begin{document}
\title{Quantum Machine Learning\\
{\Large Opportunities and Challenges}
\thanks{Prof. Debanjan Bhowmik}
}
\author{\IEEEauthorblockN{%1\textsuperscript{st}
Rathour Param Jitendrakumar}
\IEEEauthorblockA{190070049\\\textit{Department of Electrical Engineering} \\
\textit{Indian Institute of Technology Bombay}\\
paramrathour@ee.iitb.ac.in}
}

\maketitle 

\begin{abstract}
% Though there are advancements in quantum computing technology, 
Nowadays, a general purpose quantum computer seems closer to reality than ever before, yet, it is so far. Can the near-term quantum technologies create an impact on ML and guide us towards quantum supremacy?
This report contains an introduction to machine learning and quatum mechanics. We also discuss a quantum algorithm to solve linear system of equations and then move onto discussing Quantum-Assisted Machine Learning, its the opportunities and challenges in the near-term future.
\end{abstract}
\begin{IEEEkeywords}
quantum computing, machine learning, quantum machine learning, quantum-assisted machine learning, near-term quantum computers, quantum-assisted Helmholtz machines
\end{IEEEkeywords}

\section{Introduction}
Quantum Computing truly has the potential but, when will it live up to the (rising) expectations?
There has been a steady progress in this field, from increasing qubits to the increase in algorithms and design techniques. Popular quantum computing algorithms, e.g, Shor's algorithm, Grover's algorithm, Deutsch-Jozsa, BB84 Protocol, Quantum Fourier Transform and others have all been instrumental achievements in their fields. But in Machine Learning there is no such defining algorithm yet. Is their a feasible Quantum Approach for Machine Learning (ML) in near-term future? The estimated number of qubits in near-term future is 100-1000 which unfortunately is not sufficient for large ML tasks. We will focus on quantum approaches on a very promising field of unsupervised ML after getting comfortable with all the basics.
\input{ML.tex}
\input{QMbasics.tex}
\input{QMapplication.tex}
% \clearpage
\input{QMFuture.tex}
\input{QMOpportunities.tex}
% \clearpage
\input{QMChallenges.tex}
\section{Quantum-Assisted Helmholtz Machine (QAHM)}
A hybrid quantum–classical ML which can potentilly handle real-world datasets. Its made of a  generator network and a recognition network using the notion of stochastic hidden variables. Classification can also be implemented in QAHM.
% \clearpage
% \section*{Acknowledgment}
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{references}
\end{document}